Towards open collaboration in biomedical and health research: A scoping review

### 2023-09-15 doc/paper.qmd
updated contributions
note about not using WOSR

-   **Original timeline**: We were quite ambitious with the timeline for
    completing this scoping review. We did not adhere to the timeline.
-   **API vs web search results**: Almost all source databases had
    exposed APIs, with R packages available to access them. We chose to
    use these rather than using the web to extract the source data is
    due to our secondary aim. However, we noticed that there were some
    small differences in search results between the API query compared
    to the web-based query. We can't explain these differences, though
    they were quite minor.

@@

HC: MG: DBI: LWJ:

>>>>

-   **Original timeline**: We were quite ambitious with the timeline for
    completing this scoping review. We did not adhere to the timeline.
-   **API vs web search results**: Almost all source databases had
    exposed APIs, with R packages available to access them. We chose to
    use these rather than using the web to extract the source data is
    due to our secondary aim. However, we noticed that there were some
    small differences in search results between the API query compared
    to the web-based query. We can't explain these differences, though
    they were quite minor.
-   **Exclude Web of Science source**: We were unable to connect the Web
    of Science source to R through the `{wosr}` package. Using the API
    key did not as documented in the package did not work. We decided
    that in the interest of reproducibility, that we exclude this
    source.

@@

-   HC:
-   MG:
-   DBI: Conceptualization, Data curation, formal analysis,
    investigation, methodology, writing
-   LWJ:
